Your Title Goes Here...

### 2024-01-11 conclusion.tex
Update template

Conclusion goes here\dots{}

@@

\section*{Acknowledgements}

@@

>>>>

Conclusion goes here\dots{}
This section should provide a brief summary of the paper.
It should also highlight the contributions of the paper,
and discuss the implications of it.

@@

\section*{Acknowledgements}\label{sec:acknowledgements}

@@

% An example snippet of acknowledgements:
\begin{comment}
    This research is supported
    by National Natural Science Foundation of China
    (\numero{62376263}),
    and Basic Research Program of Shenzhen
    (\numero{JCYJ20230807140507015}).
\end{comment}
